What We Eval in the Shadows

### 2021-04-17 paper/main.tex
Update in 6

Finally, let us mention an anecdotal use of \eval as a mean to bypass some
checks performed by the \c{R CMD CHECK} tool allowing one to submit a package
to CRAN that would otherwise be refused. For example, the tool checks that
packages do not call \c{unlockBinding} function.\footnote{It allows one to open
and modify loaded package name space.} Packages such as \c{data.table}
circumvent such restrictions by using \eval as the check is only performed
statically.

>>>>

Finally, let us mention an anecdotal use of \eval as a mean to bypass some
checks performed by the \c{R CMD CHECK} tool. This tool performs a numer of
well-formedness rules before accepting a package to the CRAN repository. Many
checks are performed statically, by looking at syntactic constructs in the R
code. Using \eval allows one to bypass such checks and thus submit a package to
CRAN that would otherwise be refused. For example, the it checks that packages
do not call \c{unlockBinding} function.\footnote{It allows one to open and
modify loaded package name space.} Packages such as \c{data.table} circumvent
such restrictions by using \eval as the check is only performed statically.
